---
output:
  pdf_document: default
  html_document: default
---
`r if(knitr:::is_latex_output()) '\\startappendices'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'` 

<!-- If you feel it necessary to include an appendix, it goes here. The first appendix should include the commands above. -->



# Supplementary material for chapter \@ref(stonechats) {#app-stonechats-supp}

```{r, include=T, results='asis', eval=knitr::is_latex_output(),echo=F,message=F}
cat('\\newpage')
```


```{r app-zug-supp, include=T, echo=F, results='asis'}
pages <- list.files(file.path("/Users/Benjamin/Documents/Oxford/Thesis/oxforddown/pdf_chapters/zug"),pattern="zug_supp_crop_Part",full.names = T)

cat(paste0("\\begin{center} \\includegraphics[width=1\\linewidth]{",pages,"} \\end{center} \\newpage \n"))
```






# Supplementary material for chapter \@ref(lights) {#app-lights-supp}

<!-- \hypertarget{app-lights-supp}{ -->
<!-- \chapter{Supplementary Material for Chapter {\@ref(lights)}}\label{app-lights-supp}} -->

```{r, include=T, results='asis', eval=knitr::is_latex_output(),echo=F,message=F}
cat('\\newpage')
```


```{r app-lights-supp, include=T, echo=F, results='asis'}
pages <- list.files(file.path("/Users/Benjamin/Documents/Oxford/Thesis/oxforddown/pdf_chapters/lights/supp-tables-model"),pattern="lights_supp_crop_Part",full.names = T)


cat(paste0("\\begin{center} \\makebox[\\linewidth][c]{\\includegraphics[width=1.2\\linewidth]{", pages, "}} \\end{center} \\newpage \n"))
```






```{block type='savequote', include=knitr::is_latex_output()}
Horton, K.G., **Van Doren, B.M.**, La Sorte, F.A., Cohen, E.B., Clipp, H., Buler, J.J., Fink, D., Kelly, J.F., and Farnsworth, A. (2019). Holding steady: Little change in intensity or timing of bird migration over the Gulf of Mexico. *Global Change Biology*. 25, 1106-1118. 
```

\hypertarget{app-gulf}{
\chapter[Timing and intensity of bird migration over the Gulf of Mexico]{Little change in intensity or timing of bird migration over the Gulf of Mexico}\label{app-gulf}}

```{r, include=T, results='asis', eval=knitr::is_latex_output(),echo=F,message=F}
cat('\\newpage')
```


```{r app-gulf, include=T, echo=F, results='asis'}
pages <- list.files(file.path("/Users/Benjamin/Documents/Oxford/Thesis/oxforddown/pdf_chapters/app-gulf"),
                    pattern="app-gulf_Part",full.names = T)


cat(paste0("\\begin{center} \\makebox[\\linewidth][c]{\\includegraphics[width=1.15\\linewidth]{", pages, "}} \\end{center} \\newpage \n"))

```





```{block type='savequote', include=knitr::is_latex_output()}
Horton, K.G., **Van Doren, B.M.**, La Sorte, F.A., Fink, D., Sheldon, D., Farnsworth, A., and Kelly, J. (2018). Navigating north: how body mass and winds shape avian flight behaviors across a North American migratory flyway. *Ecology Letters*. 21, 1055-1064.
```

\hypertarget{app-plains}{
\chapter[Avian flight behaviors across a North American flyway]{Navigating north: how body mass and winds shape avian flight behaviors across a North American migratory flyway}\label{app-plains}}


```{r, include=T, results='asis', eval=knitr::is_latex_output(),echo=F,message=F}
cat('\\newpage')
```


```{r app-plains, include=T, echo=F, results='asis'}
pages <- list.files(file.path("/Users/Benjamin/Documents/Oxford/Thesis/oxforddown/pdf_chapters/app-plains"),
                    pattern="app-plains_Part",full.names = T)


cat(paste0("\\begin{center} \\makebox[\\linewidth][c]{\\includegraphics[width=1.2\\linewidth]{", pages, "}} \\end{center} \\newpage \n"))

```








```{block type='savequote', include=knitr::is_latex_output()}
Horton, K.G., Nilsson, C., **Van Doren, B.M.**, La Sorte, F.A., Dokter, A.M., and Farnsworth, A. (2019). Bright lights in the big cities: migratory birds’ exposure to artificial light at night. *Frontiers in Ecology and the Environment* 17, 209-214.
```

\hypertarget{app-city-lights}{
\chapter[Migratory birds’ exposure to artificial light at night]{Bright lights in the big cities: migratory birds’ exposure to artificial light at night}\label{app-city-lights}}


```{r, include=T, results='asis', eval=knitr::is_latex_output(),echo=F,message=F}
cat('\\newpage')
```


```{r app-city-lights, include=T, echo=F, results='asis'}
pages <- list.files(file.path("/Users/Benjamin/Documents/Oxford/Thesis/oxforddown/pdf_chapters/app-city-lights"),
                    pattern="app-city-lights_Part",full.names = T)


cat(paste0("\\begin{center} \\makebox[\\linewidth][c]{\\includegraphics[width=1.2\\linewidth]{", pages, "}} \\end{center} \\newpage \n"))

```




